Model-based variable selection for regression with highly correlated variables.

### 2014-09-11 www/article.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@841 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{hyp}\label{H1}
In order to take into account the covariates correlation problem, we make the hypothesis correlation between covariates is {\it only} the consequence that some covariates {\it linearly} depend on some other covariates. More precisely, there are $d_{r}\geq 0$ such ``sub-regressions'', each sub-regression $j=1,\ldots,d_{r}$ having the covariate $\boldsymbol{X}^{J_{r}^j}$ as {\it response} variable ($J_{r}^j\in\{1,\ldots,p\}$ and $J_{r}^j\neq J_{r}^{j'}$ if $j\neq j'$) and having the $d_p^j>0$ covariates $\boldsymbol{X}^{J_{p}^j}$  as {\it predictor} variables ($J_{p}^j\subset\{1,\ldots,d\} \backslash J_{r}^j$ and $d_p^j=|J_{p}^j|$ the cardinal of $J_{p}^j$):
\begin{equation}
\boldsymbol{X}^{J_{r}^j}|\boldsymbol{X}^{J_{p}^j};\boldsymbol{\alpha}_j,\sigma^2_j=\boldsymbol{X}^{J_{p}^j}\boldsymbol{\alpha}_j+\boldsymbol{\varepsilon}_j, \label{eq:SR}
\end{equation}
where $\boldsymbol{\alpha}_j\in{\mathbb{R}^{d_r^j}}$ (${\alpha}_j^h\neq 0$ for all $j=1,\ldots,d_r$ and $h=1,\ldots,d_p^j$) and $\boldsymbol{\varepsilon}_j \sim\mathcal{N}_n(\boldsymbol{0},\sigma^2_j\boldsymbol{I})$.
\end{hyp}

>>>>

\begin{hyp}\label{H1}
In order to take into account the covariates correlation problem, we make the hypothesis correlation between covariates is {\it only} the consequence that some covariates {\it linearly} depend on some other covariates. More precisely, there are $d_{r}\geq 0$ such ``sub-regressions'', each sub-regression $j=1,\ldots,d_{r}$ having the covariate $\boldsymbol{X}^{J_{r}^j}$ as {\it response} variable ($J_{r}^j\in\{1,\ldots,d\}$ and $J_{r}^j\neq J_{r}^{j'}$ if $j\neq j'$) and having the $d_p^j>0$ covariates $\boldsymbol{X}^{J_{p}^j}$  as {\it predictor} variables ($J_{p}^j\subset\{1,\ldots,d\} \backslash J_{r}^j$ and $d_p^j=|J_{p}^j|$ the cardinal of $J_{p}^j$):
\begin{equation}
\boldsymbol{X}^{J_{r}^j}|\boldsymbol{X}^{J_{p}^j};\boldsymbol{\alpha}_j,\sigma^2_j=\boldsymbol{X}^{J_{p}^j}\boldsymbol{\alpha}_j+\boldsymbol{\varepsilon}_j, \label{eq:SR}
\end{equation}
where $\boldsymbol{\alpha}_j\in{\mathbb{R}^{d_r^j}}$ (${\alpha}_j^h\neq 0$ for all $j=1,\ldots,d_r$ and $h=1,\ldots,d_p^j$) and $\boldsymbol{\varepsilon}_j \sim\mathcal{N}_n(\boldsymbol{0},\sigma^2_j\boldsymbol{I})$.cf
\end{hyp}
